\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-23 paper.tex
admission algorithm

\usepackage{pifont}
\usepackage{amssymb}
\newtheorem{definition}{\noindent{\bf Definition}}
%\newtheorem{lemma}{\noindent{\bf Lemma}}
%\newtheorem{theorem}{\noindent{\bf Theorem}}
%\newtheorem{proposition}{\noindent{\bf proposition}}
\usepackage{appendix}
\usepackage[ruled, vlined , linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amsmath,bm}
\usepackage{enumerate}
\usepackage{footnote}
\makesavenoteenv{table}

@@

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(est) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
\multirow{3}{*}{$d\!=\!(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs} \\
\hline
$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{When an admitted demand finishes, it will be removed from $\hat{D}$.} }\\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$\hat{D}$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$c_e, c_t$ &\multicolumn{6}{|l}{the remaining capacity on link $e$ or a tunnel $t$}\\
\hline
$\mathbf{z}\in Z$ &\multicolumn{6}{|l}{a network failure scenario in the scenario set}\\
\hline
$p_{\mathbf{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\mathbf{z}$ occurs}\\
\hline
$v_t^{\mathbf{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\mathbf{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\subsection{Abstraction of bandwidth availability}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
%Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a customer demanding Inter-DC WAN bandwidth resourses could be any application or tenant  spanning multiple DCs, in either a public or a private cloud. 
%a tenant of a public cloud (e.g., Amazon AWS), who uses this substrate to build his own virtual private cloud over multiple DCs, or could be a service team who launches multiple VM instances in a private cloud (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
%Services have different bandwidth demands as well as availability targets.
%Currently, there is no interface for tenants to specify bandwidth availability.
Our abstraction of network failure scenarios and bandwidth availability demands in $\mathsf{BATE}$ are as follows.

\textbf{Network failure scenario model:} 
%$\mathsf{BATE}$ relies on network operators to provide link failure probabilities.
%A series of failure events (e.g., power outage, configuration mistakes, firmware bugs) directly lead to link failures.
%%According to the report of Google \cite{evole}, more than 90\% of the failure events can lead to high packets losses, or blackholes to entire data centers and they might occur anytime.
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
%For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1min).
%The link up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
%Inspired by the site reliability engineering (SRE) technology\cite{jointfailure,overview}, we propose a general failure model.
The Inter-DC WAN is modeled as a directed graph $G(V,E)$, where the set of nodes $V$ represent the DCs, 
and the set of links $V$ represent directed links between them. 
A network scenario $\mathbf{z}=\{mathbf{z}_1,mathbf{z}_2,...,mathbf{z}_{|E|}\}$ is a vector of link states, 
where each element $mathbf{z}_i \in \{0,1\}$ denotes whether the $i$-th link is up ($mathbf{z}_i=1$) or down ($mathbf{z}_i=0$), 
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
and we also assume network operators can use historical data to estimate the failure probability $x_i$ for this link. 
%can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1 min).
%probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
Let $Z$ denote the network scenario set and $p_{\mathbf{z}}$ is the probability that a scenario $\mathbf{z}\in Z$ may happen.
%Each link is up with the probability of $p_i$. \cite{Teavar}
%Let $z_i'$ denote the value of $z_i$, and assume link failures are independent.
Then, the expected probability that network scenario  $\mathbf{z}$ will happen \cite{Teavar} is given by 
\begin{eqnarray} \label{state}
%p_{\mathbf{z}}&=&p\left( z_1=z_1',z_2=z_2',z_3=z_3',...,z_{e}=z_{e}'\right)\nonumber \\
p_{\mathbf{z}}&=&\prod_{i=1}^{|E|}(\mathbf{z}_i \times (1-x_i)+ (1-\mathbf{z}_i)(x_i))
\end{eqnarray}

\textbf{To be updated, follow Fig.1 )
For example, an inter-DC WAN contains three links $E=\{e_1,e_2,e_3\}$. 
Network scenario $\{1,1,0\}$ means $e_1$ ,$e_2$ are available and  $e_3$ fails.
If the up probability of $e_1,e_2,e_3$ are 0.9, 0.8, 0.85, respectively.
Then its probability $p(\{1,1,0\}) =0.9\times0.8\times0.15=0.108$.

\textbf{BA demand model:}
%We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are nodes and link sets.
Let $K$ denote the set of all source-destination (s-d) DC pairs.
%Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
%DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
%\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
%&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
%&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%A bandwidth availability demand $d$ is in the form of $(\mathbf{b}_d, \beta_d,t_d^s,t_d^e)$,
A bandwidth availability demand $d$ is in the form of $(\mathbf{b}_d, \beta_d)$,
where $\mathbf{b}_d$ is a vector $<\mathbf{b}_d^1, \mathbf{b}_d^2, ...>$ of bandwidth demands over all s-d pairs \footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}.
%where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

@@

\textbf{Traffic engineering model:}
Our Traffic Engineering uses tunnel-based forwarding \cite{FFC,swan,Teavar}.%where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each source-destination node pair $k\in K$ of the inter-DC WAN, we pre-compute a set of tunnels $T_{k}$ with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}, etc.). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a sequence of links and $u_t^e$ denotes whether tunnel $t$ passes a specific link $e \in E$ or not.
%The network scenario set is $\mathbf{z}$ and the corresponding probability is $p_{\mathbf{z}}, \forall \mathbf{z}\in Z $.
We use $D$ and $\hat{D}$ to represent arrived demands and \textit{admitted} demands, respectively.
Given a demand $d$, our traffic engineering scheme will decide whether to admit it (i.e., $g_d$), 
and the bandwidth that will be allocated for an admitted demand $d \in \hat{D}$ over tunnel $t$ will be $f_d^t$.
Under the above network failure scenario model, we also use 
$v_t^{\mathbf{z}}$ to denote whether tunnel $t$ is available (i.e., $v_t^{\mathbf{z}}=1$)  or not  (i.e., $v_t^{\mathbf{z}}=0$) under the network scenario $\mathbf{z}$. 
Given an allocation result ${f_d^t | \foreach t \in T_k, k \in K}$, 
if (1) the total bandwidth allocated for each s-d pair $k$, i.e., $\sum_{\foreach t \in T_k} f_d^t}$, 
is equal to the bandwidth demand $\mathbf{b}_d^k$ for that pair, and 
(2) for every tunnel $t$ that is used in the allocation (i.e., $\f_d^t>0$), 
its expected availability under all possible network failure scenarios, 
i.e., $\sum_{\mathbf{z}} \in Z} p_{\mathbf{z}} \times v_t^{\mathbf{z}} $, 
is no less than the availability demand $\beta_d$, 
then we say this BA demand is satisfied by this exact allocation result in a probabilistic sense. 
If a failure indeed occurs, our traffic engineering scheme will try to reroute traffic that is affected by this failure. If any availability target is violated, a refund will be given back to the customer (see $\S$\ref{background}), and we use $h_d$ to denote the profit (after refunding) for demand $d$.

@@

%\subsection {Traffic Engineering for Diverse Availability Targets }\label{BATE}
%Based on the the network scenarios, we design our traffic engineering algorithm that optimizes bandwidth-based availability for diverse services.
%To this end, we introduce the problem formulation of $\mathsf{BATE}$ problem and

\subsection {Admission control} \label{admission_control}
User demands are served in a first-come-first-service (FCFS) manner without preemption.
When a new demand $d$ arrives, we have $D= $\hat{D}$ \cup {d}$.
%The Admission control  \textit{determines whether availability target of $\forall d \in D$ can be supported simultaneously subject to network failure model}.
%If this is true, the new arrival demand can be admitted, otherwise, it is rejected.
To accommodate as many demands as possible, the optimal admission strategy would be that, 
if every demand in $D$ can meet its availability target, then $d$ should be admitted. 
Otherwise, it should be rejected.
This can be modeled by a 0-1 Mixed-Integer Linear Programming (MILP) problem which  
maximizes the number of demands whose availability targets can be satisfied.
Appendix \ref{admission_problem} shows the formulation of this problem, 
which can be proved to be NP-hard by reducing the all-or-nothing multi-commodity flow problem \cite{inproceedings2} to a special case of it.
%The details are omitted for brevity.
%If availability target of $\forall d \in D$ can be supported simultaneously subject to network failure model, the new arrival demand can be admitted, otherwise, it is rejected.
%If , we can model the 
%The Admission control part decides whether a new demand submitted by a tenant can be admitted or not.

%Solving the optimization problem shown in Appendix \ref{admission_problem} can determine whether the new coming tenant's demand can be admitted.
%However,  the large size of network scenarios and 
However, in order to support agile deployment of new applications and services, 
user demands should be admitted as soon as possible, 
while the time needed to exactly sovle this NP-hard problem may be prohibitive, 
Therefore, we need a better tradeoff between efficiency and optimality.
The final admission control strategy we use is as follows:

@@

\begin{enumerate}
    \item When a new demand $d$ arrives, we fix the bandwidth allocation for all admitted demands in $\hat{D}$, then we check whether $d$ can be satisfied by the remaining network capacity and failure  probability. If the answer is positive, then admit $d$ and make a first-time bandwidth allocation for it.
    \item Otherwise, run a greedy algorithm (Algorithm \ref{greedy-1}) to conjecture whether the admitted demands can potentially be rescheduled to accommodate $d$. If the answer is positive, then admit $d$ and make a temporary bandwidth allocation for it, using the remaining network capacity as far as needed \footnote{It's possible that the temporarily allocated bandwidth falls below the demanded bandwidth, but a new allocation strategy satisfying all demands does exist (see Theorem \ref{NP-222}), and will be computed later in our periodical traffic scheduling.}. 
	\item If $d$ still cannot be accomodated, reject the demand.
%    \item Pre-allocate bandwidth to the demand with remaining network capacity and pass all the admitted demands to the traffic engineering algorithm.
\end{enumerate}

>>>>

\usepackage{pifont}
\usepackage{amssymb}
\newtheorem{definition}{\noindent{\bf Definition}}
%\newtheorem{lemma}{\noindent{\bf Lemma}}
\newtheorem{theorem}{\noindent{\bf Theorem}}
%\newtheorem{proposition}{\noindent{\bf proposition}}
\usepackage{appendix}
\usepackage[ruled, vlined , linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amsmath,bm}
\usepackage{enumerate}
\usepackage{footnote}
\makesavenoteenv{table}

@@

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(est) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
\multirow{3}{*}{$d\!=\!(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs} \\
\hline
$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived and admitted demands\footnote{When an admitted demand finishes, it will be removed from $\hat{D}$.} }\\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$\hat{D}$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$c_e, c_t$ &\multicolumn{6}{|l}{the remaining capacity on link $e$ or a tunnel $t$}\\
\hline
$\mathbf{z}\in Z$ &\multicolumn{6}{|l}{a network failure scenario in the scenario set}\\
\hline
$p_{\mathbf{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\mathbf{z}$ occurs}\\
\hline
$v_t^{\mathbf{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\mathbf{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\subsection{Abstraction of bandwidth availability}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
%Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a customer demanding inter-DC WAN bandwidth resources could be any application or tenant  spanning multiple data centers, in either a public or a private cloud. 
%a tenant of a public cloud (e.g., Amazon AWS), who uses this substrate to build his own virtual private cloud over multiple DCs, or could be a service team who launches multiple VM instances in a private cloud (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
%Services have different bandwidth demands as well as availability targets.
%Currently, there is no interface for tenants to specify bandwidth availability.
Our abstractions on network failure scenarios and bandwidth availability demands in $\mathsf{BATE}$ are as follows.

\textbf{Network failure scenario model:} 
%$\mathsf{BATE}$ relies on network operators to provide link failure probabilities.
%A series of failure events (e.g., power outage, configuration mistakes, firmware bugs) directly lead to link failures.
%%According to the report of Google \cite{evole}, more than 90\% of the failure events can lead to high packets losses, or blackholes to entire data centers and they might occur anytime.
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
%For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1min).
%The link up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
%Inspired by the site reliability engineering (SRE) technology\cite{jointfailure,overview}, we propose a general failure model.
The inter-DC WAN is modeled as a directed graph $G(V,E)$, where the set of nodes $V$ represent the data centers, 
and the set of links $E$ represent directed links between them. 
A network scenario $\mathbf{z}=\{\mathbf{z}_1,\mathbf{z}_2,...,\mathbf{z}_{|E|}\}$ is a vector of link states, 
where each element $\mathbf{z}_i \in \{0,1\}$ denotes whether the $i$-th link is up ($\mathbf{z}_i=1$) or down ($\mathbf{z}_i=0$), 
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
and we also assume network operators can use historical data to estimate the failure probability $x_i$ for this link. 
%can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1 min).
%probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
Let $Z$ denote the network scenario set, %and $p_{\mathbf{z}}$ is the probability that a scenario $\mathbf{z}\in Z$ may happen.
%Each link is up with the probability of $p_i$. \cite{Teavar}
%Let $z_i'$ denote the value of $z_i$, and assume link failures are independent.
then the expected probability that a network scenario  $\mathbf{z} \in Z$ will happen is given by \cite{Teavar} 
\begin{eqnarray} \label{state}
%p_{\mathbf{z}}&=&p\left( z_1=z_1',z_2=z_2',z_3=z_3',...,z_{e}=z_{e}'\right)\nonumber \\
p_{\mathbf{z}}&=&\prod_{i=1}^{|E|}\big(\mathbf{z}_i \times (1-x_i)+ (1-\mathbf{z}_i) \times x_i\big)
\end{eqnarray}

%\textbf{To be updated, follow Fig.1 }
Use the simple Inter-DC WAN topology in Figure \ref{motivatio_fig} as an example, where $E=\{e_1,e_2,e_3,e_4\}$.
Network scenario $\mathbf{z}=\{1,1,0,1\}$ means $e_1$ ,$e_2$, $e_4$ are working fine and  $e_3$ is down.
The expected availabilities of $e_1,e_2,e_3,e_4$ are 96\%, 99.9999\%, 99.9\%, 99.9999\%, respectively.
Then the expected availability of $\mathbf{z}$ is $p_\mathbf{z}=p_{\{1,1,0,1\}} =0.96\times0.999999\times0.001\times0.999999\simeq 0.000959998$.

\textbf{BA demand model:}
%We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are nodes and link sets.
Let $K$ denote the set of all source-destination (s-d) DC pairs.
%Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
%DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
%\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
%&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
%&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%A bandwidth availability demand $d$ is in the form of $(\mathbf{b}_d, \beta_d,t_d^s,t_d^e)$,
A bandwidth availability demand $d$ is in the form of $(\mathbf{b}_d, \beta_d)$,
where $\mathbf{b}_d$ is a vector $<\mathbf{b}_d^1, ..., \mathbf{b}_d^k, ...>$ of bandwidth demands on each s-d pair $k \in K$ \footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}.
%where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

@@

\textbf{Traffic engineering model:}
Our Traffic Engineering uses tunnel-based forwarding \cite{FFC,swan,Teavar}.
%where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each source-destination node pair $k\in K$ of the inter-DC WAN, we pre-compute a set of tunnels $T_{k}$ with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}, etc.). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a sequence of links and $u_t^e$ denotes whether tunnel $t$ passes a specific link $e \in E$ or not.
%The network scenario set is $\mathbf{z}$ and the corresponding probability is $p_{\mathbf{z}}, \forall \mathbf{z}\in Z $.
We use $D$ and $\hat{D}$ to represent \textit{arrived} demands and \textit{admitted} demands, respectively.
Given a new demand $d$, our admission control scheme will decide whether to admit it, 
and the bandwidth that will be allocated for an admitted demand $d \in \hat{D}$ 
over tunnel $t$ is denoted by $f_d^t$.

With the above network failure scenario model, we also use 
$v_t^{\mathbf{z}}$ to denote whether tunnel $t$ is available (i.e., $v_t^{\mathbf{z}}=1$)  or not  (i.e., $v_t^{\mathbf{z}}=0$) under network scenario $\mathbf{z}$. 
Given a BA demand $d\!=\!(\mathbf{b}_d, \beta_d)$, an allocation result $\{f_d^t\}$ and a network scenario $\mathbf{z}$, 
\textbf{for each s-d pair} $k$, 
if the total allocated bandwidth on available tunnels under $\mathbf{z}$, 
i.e., $\sum_{\forall t \in T_k} f_d^t v_t^{\mathbf{z}}$,  
is no less than the bandwidth demand $\mathbf{b}_d^k$, 
then we call $\mathbf{z}$ a \textit{qualified scenario} for allocation $\{f_d^t\}$ with respect to demand $d$, 
and denote this by $\mathbf{z} \propto <d, \{f_d^t\}>$.
The sum of the probabilities of all such qualified scenarios, i.e., $\sum_{\mathbf{z} \propto <d, \{f_d^t\}>} p_{\mathbf{z}}$, is the expected probability that the bandwidth target $\mathbf{b}_d$ will be satisfied.
Now we can formally define when a bandwidth availability demand is satisfied: a demand $d$ is satisfied by an allocation $\{f_d^t\}$, if and only if 
\[
\sum_{\mathbf{z} \propto <d, \{f_d^t\}>} p_{\mathbf{z}} \ge \beta_d
\].

\iffalse
Given an allocation result $\{f_d^t\}$, 
(i) if the total bandwidth allocated for \textbf{each} s-d pair $k$ through the total surviving tunnels under network scenario $\mathbf{z}$, i.e., $\sum_{\forall t \in T_k} f_d^tv_t^{\mathbf{z}}$, 
is not smaller than demand $\mathbf{b}_d^k$ for that pair under under scenario $\bm{z}$,  then we call the scenario as a qualified one;
(ii) The sum of qualified scenario probability can be seen as the achieved availability and if the achieved availability
%(ii) for every tunnel $t$ that is used in the allocation (i.e., $f_d^t>0$), 
%its expected availability under all possible network failure scenarios, 
%i.e., $\sum_{\mathbf{z}} \in Z p_{\mathbf{z}} \times v_t^{\mathbf{z}} $, 
is no less than the availability demand $\beta_d$, then we say this BA demand is \textbf{satisfied} by this exact allocation result. 
\fi

If a failure indeed occurs, our failure recovery scheme will try to reroute traffic that is affected by this failure. If any availability target is violated, a refund will be given back to the customer (see $\S$\ref{background}) according to the achieved availability, and we use $h_d$ to denote the profit (after refunding) for serving demand $d$.

@@

%\subsection {Traffic Engineering for Diverse Availability Targets }\label{BATE}
%Based on the the network scenarios, we design our traffic engineering algorithm that optimizes bandwidth-based availability for diverse services.
%To this end, we introduce the problem formulation of $\mathsf{BATE}$ problem and 
 \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}} 
\KwOut{Whether the new demand can be admitted.}
%$g_d=0, s_d=1, \forall d \in D$; \\
%$f_{d}^t = 0, \forall d \in D ,  k\in K: t\in T_{k}$;\\
\While{$true$}{
$d=\arg_{d'\in D}min\{\sum_{k\in K}b_{d'}^k\times \beta_{d'}\}$;\\
\For{$k\in K$}{
\If{$b_{d}^k >$  remaining capacity of s-d pair $k$}{
    \Return $ False$;\\
}
$T'_k=T_k$;\\
\While{$b_{d}^k>0$}{
$t=\arg_{t\in T'_k}{\min\{c_t*p_t\}}$;\\
 $f_{d}^t=\min$\{$c_t$, $b_{d}^k$\};\\
$ T'_k=T'_k \setminus t$;\\
 $s_d=s_d*p_t$;\\
 $b_{d}^k = b_{d}^k- f_{d}^t;$\\
  $c_t= c_t- f_{d}^t;$\\
}
%\For{$t\in T_k$}{
%   $f_{d}^t=Allocation(t, \mathbf{b}^k_d)$;\\
%   \If{$f_{d}^t>=0$}{
%   $s_i=s_i*p_t$;\\
%   $\mathbf{b}^k_d = \mathbf{b}^k_d- f_{d}^t;$\\
%   }
%   \If{$\mathbf{b}^k_d<=0$}{
%   \textbf{break};\\
%   }
%}
}
  \If{$s_d <   \beta_{d}$}{
      \Return $False$;\\
  }
  $D=D\setminus d$;\\
}

\Return $True$;\\
\caption{Admission Conjecture}
\label{greedy-1}
\end{algorithm}
\subsection {Admission control} \label{admission_control}
User demands are served in a first-come-first-service (FCFS) manner without preemption.
When a new demand $d$ arrives, we have $D= \hat{D} \cup {d}$.
%The Admission control  \textit{determines whether availability target of $\forall d \in D$ can be supported simultaneously subject to network failure model}.
%If this is true, the new arrival demand can be admitted, otherwise, it is rejected.
To accommodate as many demands as possible, the optimal admission strategy would be that, 
if every demand in $D$ can meet its availability target, then $d$ should be admitted. 
Otherwise, it should be rejected.
This can be modeled by a 0-1 Mixed-Integer Linear Programming (MILP) problem which  
maximizes the number of demands whose availability targets can be satisfied.
Appendix \ref{admission_problem} shows the formulation of this problem, 
which can be proved to be NP-hard by reducing the all-or-nothing multi-commodity flow problem \cite{inproceedings2} to a special case of it.
%The details are omitted for brevity.
%If availability target of $\forall d \in D$ can be supported simultaneously subject to network failure model, the new arrival demand can be admitted, otherwise, it is rejected.
%If , we can model the 
%The Admission control part decides whether a new demand submitted by a tenant can be admitted or not.

%Solving the optimization problem shown in Appendix \ref{admission_problem} can determine whether the new coming tenant's demand can be admitted.
%However,  the large size of network scenarios and 
However, in order to support agile deployment of new applications and services, 
user demands should be admitted as fast as possible, 
while the time needed to exactly solve this NP-hard problem may be prohibitive, 
Therefore, we need a better tradeoff between efficiency and optimality.
The final admission control strategy we use is as follows:

@@

\begin{enumerate}
    \item When a new demand $d$ arrives, we \textit{fix} the bandwidth allocation for all admitted demands in $\hat{D}$, then we check whether $d$ can be satisfied by the remaining network capacity and failure  probability. If the answer is positive, then admit $d$ and make a first-time bandwidth allocation for it.
    \item Otherwise, run a greedy algorithm (Algorithm \ref{greedy-1}) to conjecture whether the admitted demands can potentially be rescheduled to accommodate $d$. If the answer is positive, then admit $d$ and make a temporary bandwidth allocation for it, using the remaining network capacity as far as needed \footnote{It's possible that the temporarily allocated bandwidth falls below the demanded bandwidth, but a new allocation strategy satisfying all demands does exist (see Theorem \ref{NP-222}), and will be computed later in our periodical traffic scheduling.}. 
	\item If $d$ still cannot be accommodated, reject the demand.
%    \item Pre-allocate bandwidth to the demand with remaining network capacity and pass all the admitted demands to the traffic engineering algorithm.
\end{enumerate}
